Peridynamic Plates and Flat Shells: A non-ordinary, state-based model

### 2014-05-05 PlatePaper.tex
added double-torsion test

\section{Introduction}
\todo{Lets not start this paper with the exact same sentence as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.  When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.  Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.  Other peridynamic models capture tension and compression in 1D bars \cite{silling2003deformation} and 2D membranes \cite{silling2005peridynamic}, but these features do not resist transverse displacement.  A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.  This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading.  The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
A nonlocal plate model by Ansari et al. \cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.

@@

%
\section{Peridynamics}
\label{sec:PDintro}
\todo{Again, not word-for-word} The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he originally developed in \cite{silling2000reformulation}.  Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.  These higher-order derivatives impose stronger continuity requirements than the classical models.  By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation 
%
\begin{equation}
    \label{eq:PDCoPV}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) {\rm d}V_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
\end{equation}
%
rather than the classical \textit{partial-differential equation}.  Instead of the divergence of stress, we have the integral of a ``force'' functional $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$.  This force functional may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.  While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity, foster2011energy, jogrady2014a}\todo{Cite several more papers here.}.

To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.

Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.  The most common states are \emph{scalar-states} and \emph{vector-states} which are scalar and vector valued, respectively.

@@

Conservation of linear momentum in the \textit{state-based} peridynamic formulation results in the equation of motion,
%
\begin{equation}
    \label{eq:PDstateEoM}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),\notag
\end{equation}
%
in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} for a displacement field \(\mathbf{u}\). 
%
\begin{equation}
    \label{eq:PDdeformation}
    \vstate{Y}{\mathbf{x}}{\mathbf{q}-\mathbf{x}} = (\mathbf{q}-\mathbf{x}) + (\mathbf{u}(\mathbf{q})-\mathbf{u}(\mathbf{x}))
\end{equation}
%

Just as stress and strain are work conjugate, so too are the force and deformation vector-states for hyperelastic materials.  If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  Models in which they are not in the same direction are called \textit{non-ordinary}.  Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.  Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
%
%\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.  These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
    \caption{Illustration of a bond pair model that resists angular deformation.}
    \label{fig:SimpleBondpair}
\end{figure}
%
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \todo{Need to define $\boldsymbol{\xi}$ somewhere} \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative. For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
%
\begin{align}
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
%
&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
\end{align}
%
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}.  The moment that resists the change in angle between partner bonds is proportional to the sine of the angle between them, therefore the force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
    \caption{Illustration of a bond pair on a plate.}
    \label{fig:BondPairPlate}
\end{figure}
%
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{bondPairV.eps_tex}
    \caption{Deformation and force vector states}
    \label{fig:Bondpair}
\end{figure}
%
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small.  Because the potential energy and force-states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}.  Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.

\subsection{Energy Equivalence}
%
To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Kirckhoff plate in the \emph{local limit}, i.e. when the nonlocal length scale vanishes.  We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and the plate thickness does not change with deformation.  While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations.  For small vertical displacements we have
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{z(\mathbf{x}+\boldsymbol{\xi})-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi})}{|\boldsymbol{\xi}|},
    \label{eq:beamdtheta}
\end{equation}
%
where $z$ is the vertical displacement of material point.  Taking \(\boldsymbol{\xi}=\xi (\cos(\phi),\sin(\phi))\) in cartesian coordinates and momentarily assuming continuous displacements for the sake of comparison, we use a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta}) about \(\xi = 0\) 
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{\xi}{2} \left(\cos^2(\phi) \kappa_1+\sin^2(\phi) \kappa_2+2\sin(\phi)\cos(\phi)\kappa_3\right)+\mathcal{O}(\xi^3)
    \label{eq:beamdtheta2}
\end{equation}
%
with
%
\begin{equation}
    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
\end{equation}
%
substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
%
\begin{align}
%\label{eq:continuousBeamw}
    w =& \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
    =& \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
    & +4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
\end{align}
%
If we use a weighting function \(\omega(\boldsymbol{\xi})=\omega(\xi)\) and assume that the $\omega$ plays the role of a localization kernel, i.e. $\omega = 0 \; \forall \; \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic plate is
%
\begin{align}
    W =& \alpha \int_{0}^\delta\int_0^{2 \pi} w\; \xi {\rm d}\phi {\rm d}\xi ,\notag \\
    =& \alpha \frac{3\pi}{8} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)\int_{0}^\delta \omega(\xi)\xi^3{\rm d}\xi + \mathcal{O}(\delta^6).\notag 
\end{align}
\todo{It's a little unclear how $m$ arrises below from this equation.  Please see if you can make it more clear.} 
%
Equating $W$ with the classical Kirchoff plate strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
%
\begin{align}
    \lim_{\delta \to 0}  W &= \Omega, \notag \\
    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right), \notag \\
%    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
    \nu = \frac{1}{3},\:\: \alpha &= \frac{16}{3 m} \frac{G h^3}{12(1-\sfrac{1}{3})},
\label{eq:alpha}
\end{align}
%
with 
\begin{equation}
%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
    m = \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag.
\end{equation}

It should be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.

>>>>

\section{Introduction}
Modeling material failure is one of the most common challenges in mechanical engineering analysis. When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.  Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.  Other peridynamic models capture tension and compression in 1D bars \cite{silling2003deformation} and 2D membranes \cite{silling2005peridynamic}, but these features do not resist transverse displacement.  A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.  This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading.  The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
Outside of peridynamics, weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.  A nonlocal plate model by Ansari et al. \cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes even stricter continuity requirements than the classical formulation.

The peridynamic formulation of continuum mechanics defines material behavior at a point as an integral function of the behavior of nearby points. By doing so, it eliminates the need to calculate gradients of displacement (required in classical continuum mechanics) and the accompanying continuity requirements. This is particularly valuable when examining material failure, in which discontinuous displacements feature heavily. Because predicting and modeling material failure is a primary goal of many analyses, peridynamic material models have attracted significant interest, resulting in several 3D solid material models \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}. Similar models have been used to capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but using them to model bending behavior requires a discretization with several nodes through the thickness of the feature, resulting in very computationally expensive models. A recent paper by Taylor and Steigmann \cite{taylor2013two} approaches this problem by reducing a bond based 3D plate to two dimensions with an integral through the plate's thickness.  This creates a model that can represent thin structures with courser discretization. Although Taylor and Steigmann's model includes a bending term, it is demonstrated only for in-plane loading. The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.

@@

%
\section{Peridynamics}
\label{sec:PDintro}
Stewart Silling first developed the theory of peridynamics in~\cite{silling2000reformulation} to eliminate the problems associated with the undefined partial derivatives that attend the formation of cracks. The name refers to the force exerted on a point by material points a finite distance away. As a strongly nonlocal model, peridynamics casts material behavior at a point as the \textit{integral} equation 
%
\begin{equation}
    \label{eq:PDCoPV}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) {\rm d}V_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
\end{equation}
%
rather than the classical \textit{partial-differential equation}.  Instead of the divergence of stress, we have the integral of a ``force'' functional $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$.  This force functional may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.  While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and many other behaviors \cite{silling2005peridynamic, dayal2006kinetics, gerstle2007peridynamic, silling2007peridynamic, warren2009non, foster2010viscoplasticity,foster2011energy,taylor2013two,ogrady2014beams}

To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.
Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.  The most common states are \emph{scalar-states} and \emph{vector-states} which are scalar and vector valued, respectively.

@@

Conservation of linear momentum in the \textit{state-based} peridynamic formulation results in the equation of motion,
%
\begin{equation}
    \label{eq:PDstateEoM}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),
\end{equation}
%
in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} for a displacement field \(\mathbf{u}\). 
%
\begin{equation}
    \label{eq:PDdeformation}
    \vstate{Y}{\mathbf{x}}{\mathbf{q}-\mathbf{x}} = (\mathbf{q}-\mathbf{x}) + (\mathbf{u}(\mathbf{q})-\mathbf{u}(\mathbf{x}))
\end{equation}
%

Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.  If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  Models in which they are not in the same direction are called \textit{non-ordinary}.  Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but little work has touched on their use.  Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations. Recent work by O'Grady and Foster \cite{ogrady2014beams} uses a non-ordinary material model to simulate bending in 1D beams.
%
%\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector $\boldsymbol{\xi} = \mathbf{q}-\mathbf{x}\: $ emanating from a point is connected by a rotational spring to its opposite emanating from that same point.  These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
    \caption{Illustration of a bond pair model that resists angular deformation.}
    \label{fig:SimpleBondpair}
\end{figure}
%
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative. For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
%
\begin{align}
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
%
&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
\end{align}
%
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}.  The moment that resists the change in angle between partner bonds is proportional to the sine of the angle between them, therefore the force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
    \caption{Illustration of a bond pair on a plate.}
    \label{fig:BondPairPlate}
\end{figure}
%
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{bondPairV.eps_tex}
    \caption{Deformation and force vector states}
    \label{fig:Bondpair}
\end{figure}
%
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small.  Because the potential energy and force-states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}.  Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.

\subsection{Energy Equivalence}
To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Kirckhoff plate in the \emph{local limit}, i.e. when the nonlocal length scale vanishes.  We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and the plate thickness does not change with deformation.  While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations.  For small vertical displacements we have
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{z(\mathbf{x}+\boldsymbol{\xi})-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi})}{|\boldsymbol{\xi}|},
    \label{eq:beamdtheta}
where $z$ is the vertical displacement of material point.  Taking \(\boldsymbol{\xi}=\xi (\cos(\phi),\sin(\phi))\) in cartesian coordinates and momentarily assuming continuous displacements for the sake of comparison, we use a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta}) about \(\xi = 0\) 
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{\xi}{2} \left(\cos^2(\phi) \kappa_1+\sin^2(\phi) \kappa_2+2\sin(\phi)\cos(\phi)\kappa_3\right)+\mathcal{O}(\xi^3)
    \label{eq:beamdtheta2}
    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \quad \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \quad \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
%\label{eq:continuousBeamw}
    w &= \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
    &= \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
    &+ 4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
If we use a weighting function \(\omega(\boldsymbol{\xi})=\omega(\xi)\) and assume that the $\omega$ plays the role of a localization kernel, i.e. $\omega = 0 \; \forall \; \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic plate is
    W =& \alpha \int_{0}^\delta\int_0^{2 \pi} w\; \xi {\rm d}\phi {\rm d}\xi ,\notag \\
    =& \alpha \frac{3\pi}{8} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)\int_{0}^\delta \omega(\xi)\xi^3{\rm d}\xi + \mathcal{O}(\delta^6).\notag 
\todo{It's a little unclear how $m$ arrises below from this equation.  Please see if you can make it more clear.} 
Equating $W$ with the classical Kirchoff plate strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
    \lim_{\delta \to 0}  W &= \Omega, \notag \\
    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \left[ \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right) \right]_{\nu=1/3}, \notag \\
%    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
    \alpha &= \frac{2 G h^3}{3 m}, \\
    \text{with}\qquad \qquad \notag \\
    \label{eq:alpha}
%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
    m &= \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag,
where $G$ is the shear modulus, $h$ is the thickness of the plate, and we have evaluated the classical Kirchoff strain-energy at a Poisson ratio of \(\sfrac{1}{3}\) in order to solve for alpha as a constant.  Because $\alpha$ is inversely proportional to $m$, the energy does not change with varying choices for $\omega$ and $\delta$. It should be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate. We will show an extension to this model that removes this restriction in Section~\ref{sec:arbitrary}.

\subsection{Combining Bending and Extension Models}
The bond-pair bending model does not resist in-plane stretching or shear deformation because these deformations preserve the angles between opposite bonds. \todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}\todo{or you might just say: \dots does not develop membrane forces.}  If these behaviors are expected in combination with bending, a useful model must resist both in-plane and transverse deformations.  To create a plate model that also resists these deformations, i.e.\ a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.  In this model, individual bonds act as springs resisting changes in length.
%
\begin{equation}
    \label{eq:bondextension}
    \vstate{T}{}{\boldsymbol{\xi}} =\beta\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|}
\end{equation}
%
By matching the energy of a 2D material in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the shell.  Following the example of \cite{silling2007peridynamic}, we begin with a 2D material under pure in-plane shear.  In Einstein notation, the strain energy of this material is
%
%\begin{align*}
%    W^d_\text{C} &= G \; h \; \epsilon_{ij} \epsilon_{ij} = G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
%    W^d_\text{PD} &= \frac{\beta}{2}(\underline{\omega}\; \underline{\epsilon^d})\bullet \underline{\epsilon^d}\\
%    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{\underline{\omega}\langle\xi\rangle}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_\xi\\
%\end{align*}
%
\begin{align*}
    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d,  \\  \\
    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; {\rm d}A_{\boldsymbol{\xi}}, \\
    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;{\rm d}A_{\boldsymbol{\xi}},\\
    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;{\rm d}A_{\boldsymbol{\xi}}.
\end{align*}
%
where $\epsilon^d$ is the deviatoric strain tensor.  Now, to evaluate the integral we will exploit the symmetry properties. With $i, j, k, l = 1,2$. For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
%
\begin{align*}
%    m&=(\underline{\omega}\:\underline{x}) \bullet \underline{x}\\
    m &= \int_A \omega(\xi)|\boldsymbol{\xi}|^2\; dA_{\boldsymbol{\xi}} \\
    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11})]\\
    &= \frac{\beta \; m}{16} \epsilon_{ij}^d \epsilon_{kl}^d (\delta_{ij}\delta_{kl}+\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})\\
    &= \frac{\beta \; m}{8} \epsilon_{ij}^d \epsilon_{ij}^d \implies\\
     \beta &= \frac{8 \; G\;h}{m}
\end{align*}
%
Having calibrated the bond-extension model to the shear modulus, applying a different uniform strain (such as might result from uniaxial tension) reveals the bond-based model to result in a one-parameter linearly-elastic model with Poisson's ratio \(\nu=\sfrac{1}{3}\).

Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a shell.  Consider a single bond-pair in the combined model shown in Fig.~\ref{fig:hybridmodel}.
%
\begin{figure}[tbp]
  \centering
  \input{\diagrampath/bondPairCombinedV.tex}
  \caption{The Hybrid Model Combines Bending and Extension Components}
  \label{fig:hybridmodel}
\end{figure}
%
As the two sides are pulled apart, the magnitude of the extension force in each bond increases, and the magnitude of the bending force decreases.  At the same time, the angle at which the extension force acts decreases, and the angle of action for the bending force increases.  For small amounts of bending and reasonable stretches, increased tension in the direction of the bond pair results in increase restorative force.
